Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-20 Latex/journal_v1/V4/pr.tex
add

\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

@@

The problem can be solved by two different method. 
Next we introduce the first method which is a greedy algorithm.
\begin{enumerate}
\item \textit{Greedy Algorithm:}
The problem can be simplificated and reformulated as follow
\begin{subequations}\label{problem2}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{r=1}^{R}g_{u(s,i)}^r \bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & g_{u(s,i)}^r P_r \leq \zeta_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
So \eqref{problem2}, is a NP-complete 0-1 multiple knapsack problem  
\end{enumerate} 
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

So the given assumption leads to have same energy for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
The problem can be solved by two different method. 
Next we introduce the first method which is a greedy algorithm.
\begin{enumerate}
\item \textit{Greedy Algorithm:}
The problem can be reformulated as follow
\begin{subequations}\label{problem2}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\
\text{subject to} \quad  & \sum_{s=1}^{S}\sum_{i=1}^{U_s} g_{u(s,i)}^r \psi_{r,u(s,i)}\leq \mathfrak{t}_r \quad \forall r
 \label{p11} \\
& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\
 & g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{p13}  
\end{alignat}
\end{subequations}
Where $ \psi_{r,u(s,i)}=\sum_{k=1}^{K_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k}  e^k_{r,u(s,i)}$
and $\mathfrak{t}_r = \zeta_r- \sigma_r$
Since we obtained \eqref{RConstr} in \eqref{sub1}, we can ignore this constraint in \eqref{problem2}.
To simplicated  and reformulated to the multiple knapsack problem suppose that each UE in each service is associated to only one O-RU. Therefore, constraint \eqref{p12} is restricted to equality
($\sum_{r=1}^R g^r_{u(s,i)} = 1 $). By changing this constraint,
the problem \eqref{problem2} convert to an NP-complete 0-1 multiple knapsack problem.  
We solve this problem using GAAOU which is a greedy algorithm \eqref{alg1} as follow \cite{akccay2007greedy,lee2018dynamic}.
Firstly, we set all variables $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$. 
Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
as a set of O-RUs and value of each O-RU, respectively.
Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 
it does not exceed the value of each O-RU (that is a function of maximum power and capacity of O-RU).
If it exceeds the value of O-RU, then O-RU with the next highest achievable rate is selected. 
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
The complexity of this algorithm is about $O(N\times \mathfrak{N})$
\begin{algorithm}
\caption{Greedy Algorithm for Assignment of O-RU to UEs (GAAOU)}\label{alg1}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{31}
\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$
\Else
\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for} \label{34}
\end{algorithmic}
\end{algorithm}
\item\textit{Lagrangian Function:} The second method to solve the O-RU assignment is to relax $\boldsymbol{G}$ between zero and one and solve the problem using Lagrangian function.

\end{enumerate} 
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
